### 2021-04-11 Chapter-5/Chapter-5.tex
Updates from Overleaf

\subsection{Chi-squared Test}

\subsection{Threat Model and Math Notation}

@@

\begin{figure}[h]
\begin{minipage}{0.4\linewidth}
\begin{lstlisting}
void function1(uint8_t* secret)
{
  uint8_t k1, k2;
  k1 = secret[1];
  k2 = secret[2];
  if (k1 > k2)
    a();
  if (k1 + k2 < 256)
    b();
  ...
}
\end{lstlisting}\caption*{(a) Independent Leakages}
\end{minipage}
\hfill
\begin{minipage}{0.4\linewidth}
\begin{lstlisting}
void function2(uint8_t* secret)
{
  uint8_t k1, k2;
  k1 = secret[1];
  k2 = secret[2];
  if (k1 + k2 > 128)
    c();
  if (k1 > 64)
    d();
  ...
}
\end{lstlisting} \caption*{(b) Dependent Leakages}
\end{minipage}
\caption{Multiple Leakages}\label{chapter5:fig:multiple}
\end{figure}

Considering the examples in Figure~\ref{chapter5:fig:multiple}, Figure~\ref{chapter5:fig:multiple}(a) show a code snippet with two leakage sites at line 6 and line 8 respectively. For example, if an adversary observes that function \textsf{a} executes, then the attacker can infer the first byte in buffer \textsf{secret} is larger than the second byte.  Similarly, if an adversary observes that function \textsf{b} executes, then the attacker can infer that the sum of first two bytes in buffer \textsf{secret} is smaller than $256$.

@@

@@

\begin{table}[h]
  \centering
  \resizebox{0.45\textwidth}{!}{%

>>>>

\subsection{Chi-Squared Test}
A chi-squared test can determine if there is a relationship between two categorical variables. Suppose we can summarize the data in a $rxc$  two-way contingency table. The chi-square test statistic is calculated with the below formula:
\[\tilde{\chi}^2=\sum_{k=1}^{rc} \frac{(O_k - E_k)^2}{E_k}\]
$O$ is the observe value and $E$ is the expected value. A low value means that there is a high correlation between the two variables. 
\subsection{Threat Model and Math Notation}

@@

\begin{figure}[h]
\begin{minipage}{0.4\linewidth}
\begin{lstlisting}
void function1(uint8_t* secret)
{
  uint8_t k1, k2;
  k1 = secret[1];
  k2 = secret[2];
  if (k1 > k2)
    a();
  if (k1 + k2 < 256)
    b();
  ...
}
\end{lstlisting}\caption*{(a) Independent Leakages}
\end{minipage}
\hfill
\begin{minipage}{0.4\linewidth}
\begin{lstlisting}
void function2(uint8_t* secret)
{
  uint8_t k1, k2;
  k1 = secret[1];
  k2 = secret[2];
  if (k1 + k2 > 128)
    c();
  if (k1 > 32)
    d();
  ...
}
\end{lstlisting} \caption*{(b) Dependent Leakages}
\end{minipage}
\caption{Multiple Leakages}\label{chapter5:fig:multiple}
\end{figure}

Considering the examples in Figure~\ref{chapter5:fig:multiple}, Figure~\ref{chapter5:fig:multiple}(a) show a code snippet with two leakage sites at line 6 and line 8 respectively. For example, if an adversary observes that function \textsf{a} executes, then the attacker can infer the first byte in buffer \textsf{secret} is larger than the second byte.  Similarly, if an adversary observes that function \textsf{b} executes, then the attacker can infer that the sum of the first two bytes in buffer \textsf{secret} is smaller than $256$. The interesting part here is that if the attacker observes that function \textsf{a} executes, then he still has zero knowledge about the function \textsf{b}. The two leakage sites in Figure~\ref{chapter5:fig:multiple}(b) are different. If an attacker observes function \textsf{c} executes, then it is likely the attacker can observe that function \textsf{d} also executes.

@@

We use the chi-square test to check if two leakage sites are independent. Here we run the example in Figure~\ref{chapter5:fig:multiple} many times. We record the times of the observation of the execution. Because each time, the execution is independent of the previous execution. The times of the observation for each event should satisfy the normal distribution. After that, we can use the chi-squared test to test whether the two leakage sites are independent.

\begin{figure}[h]
  \begin{minipage}{0.4\linewidth}
      \begin{tabular}{rrrr}
        \toprule
        & $c$ & $c$  & total\\
        \midrule
        $d$   & 255 & 253 &     \\
        $d$   & 260  & 256 &       \\
        total &   &        \\
        \bottomrule
      \end{tabular}%
  \end{minipage}
  \hfill
  \begin{minipage}{0.4\linewidth}
      \begin{tabular}{rrrr}
        \toprule
        & $c$ & $c$  & total\\
        \midrule
        $d$   & 809 & 82 &     \\
        $d$   & 70  & 63&       \\
        total &   &        \\
        \bottomrule
      \end{tabular}%
  \end{minipage}
  \caption{}\label{chapter5:fig:con_table}
\end{figure}

@@

\begin{table}[h]
  \centering
  \resizebox{0.8\textwidth}{!}{%
